\LARGE \bf A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-04-01 paper.tex
Small update for missing word
adjusted + fixed chart label positions, distances and angles

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}": Description of the video as scraped from the video hosting website
  \item "\texttt{state}": String that describes the current labelling state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}": The title of the video from the video hosting website
  \item "\texttt{url}": Url that the video was fetched from
  \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling
  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}": The end frame of the video segment the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{bb\_fields}": All bounding-box specific data
  \begin{itemize}
    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
    \item "\texttt{resolution}": List with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
    \item "\texttt{objects}": List of all of the bounding boxes for each object in the video. An object being either a vehicle or pedestrian. Within each object, there is metadata specific to that object.
    \begin{itemize}
      \item "\texttt{id}": Unique numerical identifier that represents this object
      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
      \item "\texttt{class}": The class of the object, such as "car", "pedestrian"
      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}

@@

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Objects by class},
      ylabel={Frequency (\# of objects)},
      xtick=data,
      xticklabels from table={\byclass}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by object class}
		\label{fig:obj-by-class}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by participant},
      xlabel={Number of participants},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byactors}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by number of participants}
		\label{fig:vids-by-participant}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by agents},
      xlabel={Number of agents},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byagents}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by number of agents}
		\label{fig:vids-by-agents}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by duration},
      xlabel={Duration (in frames)},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byduration}{X},
      xticklabel style={rotate=90}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by duration}
		\label{fig:vids-by-duration}
\end{figure}

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in,trim={0 1cm 0 1cm},clip]{by-collision.png}
		\caption{All videos in database grouped by collision type}
		\label{fig:vids-by-collision}
\end{figure}

>>>>

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}": Description of the video as scraped from the video hosting website
  \item "\texttt{state}": String that describes the current labelling state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}": The title of the video from the video hosting website
  \item "\texttt{url}": Url that the video was fetched from
  \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling
  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}": The end frame of the video segment that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{bb\_fields}": All bounding-box specific data
  \begin{itemize}
    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
    \item "\texttt{resolution}": List with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
    \item "\texttt{objects}": List of all of the bounding boxes for each object in the video. An object being either a vehicle or pedestrian. Within each object, there is metadata specific to that object.
    \begin{itemize}
      \item "\texttt{id}": Unique numerical identifier that represents this object
      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
      \item "\texttt{class}": The class of the object, such as "car", "pedestrian"
      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}

@@

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Objects by class},
      ylabel={Frequency (\# of objects)},
      ymin=-50,
      ymax=1800,
      xtick=data,
      xticklabels from table={\byclass}{X},
      xticklabel style={rotate=50,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by object class}
		\label{fig:obj-by-class}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by participant},
      xlabel={Number of participants},
      ylabel={Frequency (\# of videos)},
      ymin=-5,
      ymax=175,
      xtick=data,
      xticklabels from table={\byactors}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by number of participants}
		\label{fig:vids-by-participant}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by agents},
      xlabel={Number of agents},
      ylabel={Frequency (\# of videos)},
      ymin=-10,
      ymax=270,
      xtick=data,
      xticklabels from table={\byagents}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by number of agents}
		\label{fig:vids-by-agents}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by duration},
      xlabel={Duration (in frames)},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      ymin=-5,
      ymax=130,
      xticklabels from table={\byduration}{X},
      xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos in dataset grouped by duration}
		\label{fig:vids-by-duration}
\end{figure}

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in,trim={0 1cm 0 0.5cm},clip]{by-collision.png}
		\caption{All videos in database grouped by collision type}
		\label{fig:vids-by-collision}
\end{figure}
